---
title: "case_study.Rmd"
author: "Jesus Luevano"
date: "2023-10-10"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
library(httr)
```

```{r}
library(p8105.datasets)

data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb %>%
  rename(borough = neighbourhood_group) %>%
  mutate(stars = review_scores_location /2)
```


```{r Airbnb}
# Uncompress and load the detailed NYC airbnb data
# But only keep the 2 variables of interest
#zz <- gzfile("listings.csv.gz", 'rt')   
#airbnb_location_df = 
 # read_csv(zz, header = TRUE) %>% 
  #select(id, review_scores_location)

# Read in the summary data for NYC
airbnb_listings_df =
  read_csv("nyc_airbnb.csv") %>% 
  mutate(last_review = as.Date(last_review, format = "%Y-%m-%d"))

# Combine the two datasets
#nyc_airbnb = inner_join(airbnb_location_df, airbnb_listings_df, by = "id")

# Save the data
#save(nyc_airbnb, file = "nyc_airbnb.RData")
```

## Brainstorm questions

-Where are AirBNBs expensive?
  - Borough? Neighborhood?
  - Do other factors (room type) affect price? what about rating?
- How long are AirBNBs active?
  - Are some illegal/get shut down?
-Which units have most avaliability?
-How is review score impacted by location?
- How many apts are run by one host?
  - Does that affect price?
  - Dose that vary by neighborhood?
-Where are AirBNBs?
  -Borought?

#Do some EDA
  
```{r my examples}
#Most popular neighborhoods
nyc_airbnb %>%
  group_by(borough, neighbourhood) %>%
  summarize(n_obs = n()) %>%
  arrange(desc(n_obs))

#price of most popular neighborhoods
nyc_airbnb %>%
  group_by(borough, neighbourhood, price) %>%
  summarize(n_obs = n()) %>%
  arrange(desc(n_obs))

#Costliest neighborhoods
nyc_airbnb %>%
  group_by(neighbourhood, price) %>% 
  arrange(desc(price))
```

```{r class examples}
nyc_airbnb %>%
  count(borough)

nyc_airbnb %>%
  group_by(borough) %>%
  summarize(mean_price = mean(price))

nyc_airbnb %>%
  group_by(borough, room_type) %>%
  summarize(mean_price = mean(price)) %>%
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )

nyc_airbnb %>%
  group_by(borough, room_type) %>%
  summarize(median_price = mean(price)) %>%
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  ) 

nyc_airbnb %>%
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough ~ room_type)

nyc_airbnb %>%
  filter(price >= 9500)
```

```{r}
nyc_airbnb %>%
  filter(price <1000, room_type == "Entire home/apt") %>%
  group_by(neighbourhood) %>%
  ggplot(aes(x = price)) +
  geom_histogram() + 
  facet_grid(. ~ borough)
```

```{r}
nyc_airbnb %>%
  filter(price <1000, room_type == "Entire home/apt",
         borough == "Manhattan") %>%
  group_by(neighbourhood) %>%
  summarize(
    n_apt = n(),
    mean_price = mean(price)
  ) %>%
  arrange(desc(mean_price)) 
  
nyc_airbnb %>%
  filter(price <1000, room_type == "Entire home/apt",
         borough == "Manhattan") %>%
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% #make it factor variable in order of price
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot()


library(ggridges)
nyc_airbnb %>%
  filter(price <1000, room_type == "Entire home/apt",
         borough == "Manhattan") %>%
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% #make it factor variable in order of price
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges()

```

## Try to make a map
```{r}
nyc_airbnb %>%
  filter(price <1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") %>%
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

Try something else entirely (Leaflet)
```{r}
library(leaflet)

nyc_airbnb %>%
  filter(price <1000, 
         room_type == "Entire home/apt",
         borough == "Manhattan") %>%
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(~long, ~lat)
```

